censusprocessing

### 2021-10-28 code/analysis_code/exploration.Rmd
fixing errors, building up analysis portion

```{r}
mpdata %>% ggplot(aes(x = e.coli.cfu, y = particles_l)) + geom_point() + theme(axis.text.x = element_text(angle = 90, hjust=1))
```

Something weird is giong on with the values for e.coli.cfu.

```{r}
class(mpdata$e.coli.cfu)
```

It looks like that ended up saved as a character instead of integer. Let's convert. 
# covert character to numeric
```{r}
mpdata <- mpdata %>% mutate(e.coli.cfu = as.numeric(e.coli.cfu))
class(mpdata$e.coli.cfu)
```

# try plot again
```{r}
p3 <- mpdata %>% ggplot(aes(x = e.coli.cfu, y = particles_l)) + geom_point() + theme(axis.text.x = element_text(angle = 90, hjust=1))

@@

#subset data into just distance from each WRF
wrf <- mpdata %>% select("ccwrf", "nowrf", "miwrf") 
#find minimum distance to any WRF out of all three
val <- do.call(pmin, c(wrf, na.rm = TRUE)) 
minwrf <- transform(wrf, min=val, minCol = names(wrf)[max.col(wrf == val, 'first')])

#minwrf contains the variable min, which tells us the distance from the sample site to the nearest WRF. This is all of the information that we need, so no we will re-join to the original DF
mpwrfdata <- left_join(mpdata, minwrf)

>>>>

# plot e.coli.cfu vs particles_l
```{r}
p3 <- mpdata %>% ggplot(aes(x = e.coli.cfu, y = particles_l)) + geom_point() + theme(axis.text.x = element_text(angle = 90, hjust=1))

@@

#subset data into just distance from each WRF
wrf <- mpdata %>% select("ccwrf", "nowrf", "miwrf", "site", "date") 
#find minimum distance to any WRF out of all three
val <- do.call(pmin, c(wrf, na.rm = TRUE)) 
minwrf <- transform(wrf, min=val, minCol = names(wrf)[max.col(wrf == val, 'first')])

#minwrf contains the variable min, which tells us the distance from the sample site to the nearest WRF. This is all of the information that we need, so now we will re-join to the original DF
mpwrfdata <- left_join(mpdata, minwrf)

### 2021-10-28 code/processing_code/censusprocessing.Rmd
fixing errors, building up analysis portion

# FIPS to census tract population
```{r}
library(tidycensus)
#tidycensus::census_api_key("c02ef0638e60f9d5fbb45de5219821e3a25cd7d2", install = TRUE)
get_decennial("block", state = Georgia, variables = population, year = 2019)
```

Here, we receive an error message suggesting to use NHGIS data since the most recent small census geography data is not available through `get_decennial()`.

>>>>

Here, after attemping to use `get_decennial()` we receive an error message suggesting to use NHGIS data since the most recent small census geography data is not available through `get_decennial()`.
